parental migration and adolescents educational performance

### 2022-05-28 data/Gu-thesis-script.Rmd
model summary output coef rename

```{r}
d_cl <- d_cl %>% mutate(fa.edu.year = NA)
d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
```

```{r}
d_cl <- d_cl %>% mutate(mo.edu.year = NA)
d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
```

>>>>

```
d_cl <- d_cl %>% mutate(fa.edu.year = NA)
d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
```

```
d_cl <- d_cl %>% mutate(mo.edu.year = NA)
d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
```
